### 2021-04-13 conclusion.tex
adding more on future work

Our formalism so far only captures the core of GV. In future work, we plan to explore: recursion in PGV, by integrating the works of Lindley and Morris~\cite{lindleymorris16} and Padovani and Novara~\cite{padovaninovara15}; %a~translation from Priority GV to Priority CP;
and sharing, following Balzer and Pfenning~\cite{balzerpfenning17}.

>>>>

Our formalism so far only captures the core of GV. In future work, we plan to explore: recursion in PGV, by integrating the works of Lindley and Morris~\cite{lindleymorris16} and Padovani and Novara~\cite{padovaninovara15}; or in the lines of Kobayashi and Laneve for unbounded networks~\cite{KL17}, which is a refinement of previous work by Kobayashi. %a~translation from Priority GV to Priority CP;
Another interesting future work is on sharing, following Balzer and Pfenning~\cite{balzerpfenning17}, or Voinea \etal~\cite{VoineaDG19}.
